\todo{CMSB title:Concretizing the Process Hitting into Biological Regulatory Networks} \\\rewrite{Find a new title:} \begin{itemize} \item Abstracting BRNs from PH models \item Abstracting the BRNs of a PH model \item Extracting BRNs from PH models \item ??? \end{itemize}

### 2013-05-03 main.tex
continue refactoring section 4.3
finish refactoring section 4.3
new contributions + titles

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{pro}{Property~\ref{#1}}
\newrefformat{pps}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{thm}{Theorem~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

\newdefinition{definition}{Definition}
\newdefinition{property}{Property}
\newdefinition{proposition}{Proposition}
\newdefinition{example*}{Example}
\newdefinition{example}[example*]{Example}

@@

\title{\todo{New title} Concretizing the Process Hitting into Biological Regulatory Networks}

@@

Given a PH model of a BRN, we first tackle the inference of the underlying Interaction Graph
between components.
Then the inference of corresponding Thomas' models is provided using Answer Set Programming,
which allows notably an efficient enumeration of (possibly numerous) compatible parametrizations.

In addition to giving a formal link between different approaches for qualitative BRNs modeling, 
this work emphasizes the ability of PH to deal with large BRNs with incomplete knowledge on
cooperations, where Thomas' approach fails because of the combinatorics of parameters.

\todo{Emphasis on the new contribution since CMSB.}
\end{abstract}

>>>>

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{pro}{Property~\ref{#1}}
\newrefformat{pps}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{thm}{Theorem~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{sssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\newrefformat{ex}{Example~\ref{#1}}
\def\pref{\prettyref}

\newdefinition{definition}{Definition}
\newdefinition{property}{Property}
\newdefinition{proposition}{Proposition}
\newdefinition{example}{Example}

@@

\title{
\todo{CMSB title:Concretizing the Process Hitting into Biological Regulatory Networks}
\\\rewrite{Find a new title:}
\begin{itemize}
  \item Abstracting BRNs from PH models
  \item Abstracting the BRNs of a PH model
  \item Extracting BRNs from PH models
  \item ???
\end{itemize}}

@@

Given a PH model of a BRN, we first tackle the inference of the underlying Interaction Graph
between components.
To handle wider class of models, we introduce unsigned edges to model regulations that are
more complex than simple activations or inhibitions.
Then the inference of corresponding Thomas' models is provided using Answer Set Programming,
which allows notably an efficient enumeration of (possibly numerous) compatible parametrizations.

In addition to giving a formal link between different approaches for qualitative BRNs modeling, 
this work emphasizes the ability of PH to deal with large BRNs with incomplete knowledge on
cooperations, where Thomas' approach fails because of the combinatorics of parameters.
\end{abstract}

### 2013-05-03 parts/intro.tex
new contributions + titles

The objectives of the work presented in this paper are the following.
Firstly, we show that starting from one PH model, it is possible to find back the underlying IG.
We perform an exhaustive search for the possible interactions on one component from all the
others, consistently with the knowledge of the dynamics that these interactions lead to and that are
expressed in PH.
The second phase of our work concerns the Thomas' parameters inference.
It consists in determining the nesting set (possibly too large) of the parameters which necessarily
lead to the satisfaction of the known cooperating constraints.
The resulting BRN dynamics is ensured to respect the PH dynamics, \ie no spurious transitions are
made possible by the inference.
Answer Set Programming (ASP) \cite{Baral03} turns out to be effective for these enumerative searches.

@@

\todo{Emphasis on the new contribution since CMSB.}

>>>>

The objectives of the work presented in this paper are the following.
Firstly, we show that starting from one PH model, it is possible to find back the underlying IG.
We perform an exhaustive search for the possible interactions on one component from all the
others, consistently with the knowledge of the dynamics that these interactions lead to and that are
expressed in PH.
The second phase of our work concerns the inference of Thomas' parameters.
It consists in determining the nesting set (possibly too large) of the parameters which necessarily
lead to the satisfaction of the known cooperating constraints.
The resulting BRN dynamics is ensured to respect the PH dynamics, \ie no spurious transitions are
made possible by the inference.
Answer Set Programming (ASP) \cite{Baral03} turns out to be effective for these enumerative searches.

%A major contribution from [CMSB] is the use of unsigned edges to model a wider class of models.
While the work presented in~\cite{FPIMR12-CMSB} could not handle regulations that were not strictly activations or inhibitions,
the results presented in this paper allow to study a wider class of models by using interactions of a new type: \emph{unsigned} regulations.
The benefit is that inferring an unsigned edge does not prevent the second phase of the inference,
and the method is thus conclusive on all boolean models.
\rewrite{Should we cite [CMSB]?}

@@
